Systematic studies of correlations between different order flow harmonics in Pb-Pb collisions at $\sqrt{s_{NN}}$ = 2.76 TeV

### 2018-01-18 longSC.tex
final to EB

Even though thermalization could be achieved quickly in collisions of very large nuclei and/or at extremely high energy~\cite{Kurkela:2015qoa}, the dense matter created in heavy-ion collisions may not reach full thermal or chemical equilibrium due to its finite size and short lifetime. To address such nonequilibrium many-body dynamics, the AMPT model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en} has been developed, which includes both initial partonic and final hadronic interactions and the transition between these two phases of matter.
The initial conditions in the AMPT are given by the spatial and momentum distributions of minijets and soft strings from the HIJING model~\cite{Wang:1991hta,Gyulassy:1994ew}.
For the data comparisons, three different configurations of the AMPT model have been used: the default one and string melting with and without hadronic rescattering. The input parameters used in all configurations are $\alpha_s = 0.33$ and a partonic cross section of 1.5~mb.
In the default configuration, partons are recombined with their parent strings when they stop interacting. The resulting strings are later converted into hadrons using the Lund string fragmentation model~\cite{Andersson:1986gw,NilssonAlmqvist:1986rx}.
The Lund string fragmentation parameters were set to $\alpha = 0.5$ and $b = 0.9$~GeV$^{-2}$.
In the string melting configuration, the initial strings are melted into partons whose interactions are described by the zipping parton cascade (ZPC) model~\cite{Zhang:1997ej}. These partons are then combined into the final-state hadrons via a quark coalescence model. 
In both configurations, the dynamics of the subsequent hadronic matter is described by a hadronic cascade based on a relativistic transport (ART) model~\cite{Li:2001xh} which includes resonance decays.
The string melting configuration of the AMPT without hadronic rescattering was used to study the influence of the hadronic phase on the development of the anisotropic flow.
Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably well reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low-$p_{\rm T}$ pions and kaons in central and midcentral $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was observed in a recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the flow harmonics of identified hadrons ($v_2$, $v_3$, $v_4$, and $v_5$) at $\snn=2.76$~TeV. It turns out that the radial flow in AMPT is 25\% lower than that measured at the LHC, which is responsible for this quantitative disagreement~\cite{Adam:2016nfo}. The details of the AMPT configurations used in this article and the comparisons of $p_{\rm T}$-differential $v_{n}$ for pions, kaons, and protons to the data can be found in Ref.~\cite{Adam:2016nfo}.

>>>>

Even though thermalization could be achieved quickly in collisions of very large nuclei and/or at extremely high energy~\cite{Kurkela:2015qoa}, the dense matter created in heavy-ion collisions may not reach full thermal or chemical equilibrium due to its finite size and short lifetime. To address such nonequilibrium many-body dynamics, the AMPT model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en} has been developed, which includes both initial partonic and final hadronic interactions and the transition between these two phases of matter.
The initial conditions in the AMPT are given by the spatial and momentum distributions of minijets and soft strings from the HIJING model~\cite{Wang:1991hta,Gyulassy:1994ew}.
For the data comparisons, three different configurations of the AMPT model have been used: the default one and string melting with and without hadronic rescattering. The input parameters used in all configurations are $\alpha_s = 0.33$ and a partonic cross section of 1.5~mb.
In the default configuration, partons are recombined with their parent strings when they stop interacting. The resulting strings are later converted into hadrons using the Lund string fragmentation model~\cite{Andersson:1986gw,NilssonAlmqvist:1986rx}.
The Lund string fragmentation parameters were set to $\alpha = 0.5$ and $b = 0.9$~GeV$^{-2}$.
In the string melting configuration, the initial strings are melted into partons whose interactions are described by the Zhang's parton cascade (ZPC) model~\cite{Zhang:1997ej}. These partons are then combined into the final-state hadrons via a quark coalescence model. 
In both configurations, the dynamics of the subsequent hadronic matter is described by a hadronic cascade based on a relativistic transport (ART) model~\cite{Li:2001xh} which includes resonance decays.
The string melting configuration of the AMPT without hadronic rescattering was used to study the influence of the hadronic phase on the development of the anisotropic flow.
Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably well reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low-$p_{\rm T}$ pions and kaons in central and midcentral $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was observed in a recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the flow harmonics of identified hadrons ($v_2$, $v_3$, $v_4$, and $v_5$) at $\snn=2.76$~TeV. It turns out that the radial flow in AMPT is 25\% lower than that measured at the LHC, which is responsible for this quantitative disagreement~\cite{Adam:2016nfo}. The details of the AMPT configurations used in this article and the comparisons of $p_{\rm T}$-differential $v_{n}$ for pions, kaons, and protons to the data can be found in Ref.~\cite{Adam:2016nfo}.
